Manuscript Preparation

### 2018-12-06 Houston/src/manuscript_preparation.Rmd
Update manuscript_prep.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
options(scipen = 1, digits = 2)
require(dplyr)
require(ggplot2)
require(RcppRoll)
require(markovchain) # FIX: markovchain seems not compatible with R3.5.0
require(reshape)
require(survival)
require(caret)
require(e1071)
require(randomForest)
require(kernlab)
require(SuperLearner)

@@

##Abhishek Desktop
knitr::opts_knit$set(root.dir = "D:/Github/CRIS/violation-data-analysis/") # !! CHANGE PATH TO MATCH YOUR OWN
source("D:/Github/CRIS/violation-data-analysis/Houston/src/prepare_violation.R")
source("D:/Github/CRIS/violation-data-analysis/Houston/src/roll_over.R")

##Albert Macbook
# knitr::opts_knit$set(root.dir = "~/documents/projects/violation-data-analysis") # !! CHANGE PATH TO MATCH YOUR OWN

@@

# separate predictors
x <- data.frame(labeled.data.lost.train[, c('last.quarter.lost','last.year.lost',
                                            'last.three.years.lost','last.quarter.restrict',

                                            'last.year.restrict', 'last.three.years.restrict',
                                            'last.quarter.viol','last.year.viol',
                                            'last.three.years.viol', 'last.quarter.death',
                                            'last.year.death', 'last.year.death',
                                            'last.three.years.death')])
xtest <- data.frame(labeled.data.lost.result[, c('last.quarter.lost','last.year.lost',
                                            'last.three.years.lost','last.quarter.restrict',
                                            'last.year.restrict', 'last.three.years.restrict',
                                            'last.quarter.viol','last.year.viol',
                                            'last.three.years.viol', 'last.quarter.death',
                                            'last.year.death', 'last.year.death',
                                            'last.three.years.death')])

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
options(scipen = 1, digits = 2)
require(dplyr)
require(ggplot2)
require(RcppRoll)
#require(markovchain) # FIX: markovchain seems not compatible with R3.5.0
require(reshape)
require(survival)
require(caret)
require(e1071)
require(randomForest)
require(kernlab)
require(SuperLearner)
require(ranger)

@@

##Abhishek Desktop
# knitr::opts_knit$set(root.dir = "D:/Github/CRIS/violation-data-analysis/") # !! CHANGE PATH TO MATCH YOUR OWN
# source("D:/Github/CRIS/violation-data-analysis/Houston/src/prepare_violation.R")
# source("D:/Github/CRIS/violation-data-analysis/Houston/src/roll_over.R")

##Albert Macbook
knitr::opts_knit$set(root.dir = "~/documents/projects/violation-data-analysis") # !! CHANGE PATH TO MATCH YOUR OWN

@@

# separate predictors
x <- data.frame(labeled.data.lost.train[, c('last.quarter.lost','last.year.lost',
                                            'last.three.years.lost','last.quarter.restrict',
                                            'last.year.restrict', 'last.three.years.restrict',
                                            'last.quarter.viol','last.year.viol',
                                            'last.three.years.viol', 'last.quarter.death',
                                            'last.year.death', 'last.year.death',
                                            'last.three.years.death')])
xtest <- data.frame(labeled.data.lost.result[, c('last.quarter.lost','last.year.lost',
                                            'last.three.years.lost','last.quarter.restrict',
                                            'last.year.restrict', 'last.three.years.restrict',
                                            'last.quarter.viol','last.year.viol',
                                            'last.three.years.viol', 'last.quarter.death',
                                            'last.year.death', 'last.year.death',
                                            'last.three.years.death')])
